\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-07-19 paper/eccv2020CR/final/3668/3668.tex
Final camera-ready submission.

\newcommand{\edit}[1]{\textcolor{red}{#1}}
% \newcommand{\edit}[1]{#1}

\graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
% Pages are numbered in submission mode, and unnumbered in camera-ready

@@

% CAMERA READY SUBMISSION
% \begin{comment}
\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mark Nishimura\orcidID{0000-0003-3976-254X}  \and
David B. Lindell\orcidID{0000-0002-6999-3958} \and
Christopher A. Metzler\orcidID{0000-0001-6827-7207} \and \\
Gordon Wetzstein\orcidID{0000-0002-9243-6885}}
%
\authorrunning{M. Nishimura et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Stanford University, Stanford, CA \\
\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
%******************
\maketitle

@@

\section{Introduction}
\label{sec:intro}
\input{sections/introduction}

\section{Related Work}
\label{sec:related}
\input{sections/related}

\section{Method}
\label{sec:method}
\input{sections/method}

\section{Evaluation and Assessment}
\label{sec:evaluation}
\input{sections/simulation}

\section{Experimental Demonstration}
\label{sec:prototype}
\input{sections/hardware}

\section{Discussion}
\label{sec:discussion}
\input{sections/discussion}

\clearpage
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}

>>>>

\newcommand{\edit}[1]{\textcolor{black}{#1}}
% \newcommand{\edit}[1]{#1}

% \graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
%     Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
%     Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
%     drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
%   {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
\graphicspath{{figures/}}
% Pages are numbered in submission mode, and unnumbered in camera-ready

@@

% CAMERA READY SUBMISSION
% \begin{comment}
\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mark Nishimura\orcidID{0000-0003-3976-254X}  \and
David B. Lindell\orcidID{0000-0002-6999-3958} \and
Christopher Metzler\orcidID{0000-0001-6827-7207} \and \\
Gordon Wetzstein\orcidID{0000-0002-9243-6885}}
%
\authorrunning{M. Nishimura et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Stanford University, Stanford, CA \\
\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
%******************
\maketitle

@@

\vspace{-5pt}
\section{Introduction}
\vspace{-5pt}
\label{sec:intro}
\input{sections/introduction}

\vspace{-5pt}
\section{Related Work}
\vspace{-5pt}
\label{sec:related}
\input{sections/related}

\vspace{-5pt}
\section{Method}
\vspace{-5pt}
\label{sec:method}
\input{sections/method}

\vspace{-5pt}
\section{Evaluation and Assessment}
\vspace{-5pt}
\label{sec:evaluation}
\input{sections/simulation}

\vspace{-5pt}
\section{Experimental Demonstration}
\vspace{-5pt}
\label{sec:prototype}
\input{sections/hardware}

\vspace{-5pt}
\section{Discussion}
\vspace{-5pt}
\label{sec:discussion}
\input{sections/discussion}

\vspace{-4 pt}
\subsection*{Acknowledgments}
D.L.~was supported by a Stanford Graduate Fellowship. 
C.M.~was supported by an ORISE Intelligence Community Postdoctoral Fellowship. G.W.~was supported by an NSF CAREER Award (IIS 1553333), a Sloan Fellowship, by the KAUST Office of Sponsored Research through the Visual Computing Center CCF grant, and a PECASE by the ARL.

\clearpage
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
% \bibliography{references}
\input{3668.bbl}

### 2020-07-19 paper/eccv2020CR/final/3668/sections/method.tex
Final camera-ready submission.

In this section, we describe the image formation of a diffused pulsed laser and time-resolved detector. \edit{Although our model is derived for the specific case of imaging with a single-photon avalanche diode (SPAD), the resulting image formation model equally applies to other time-resolved detectors}. We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the \edit{transient}.

%In this section, we describe the measurement model for a single-pixel time-of-flight lidar sensor under diffuse, pulsed laser illumination.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Image Formation Model of a Diffused SPAD}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{method_eccv.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses
      the input \edit{transient measurement} and an RGB image to produce an accurate depth
      map. The \edit{transient is} preprocessed to adjust for ambient photon
      detections, radiometric falloff factors, and to calibrate the bin widths.
      From the RGB image, an MDE estimates an initial depth map
      and the scene reflectance is estimated. A reflectance-weighted
      depth histogram is compared to the processed \edit{transient} to
      calculate a histogram matching matrix which is used to output the corrected depth.
  }
  \label{fig:pipeline}
\end{figure}

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates light scattered back from the scene onto the detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
diffused light, and we assume that the light is diffused uniformly over the
scene points. Each time such a light pulse is emitted into the scene and
scattered back to the detector, the single-pixel SPAD time-stamps up to one of
the returning photons with some probability. The process is repeated millions of
times per second with the specific number of emitted pulses being controlled by
the repetition rate of the laser. \edit{As derived in previous work, the resulting measurement
can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}.} Each detected photon arrival event is
discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $[n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents background detections from ambient light and false positive detections known as \textit{dark
count}. \edit{Like previous work, we neglect scene interreflections
and confine ourselves to the low-flux condition (where the number of photon
detections is controlled to be much smaller than the number of emitted pulses)
to avoid pileup~\cite{Shin2016}.} Finally, we adopt the term
\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.

@@

\vspace{0.8em}\noindent{\bf Background Subtraction.}
In the first step, we remove the background counts from the
transient by initially estimating the average amount of background counts
in each time bin. For nearly all natural scenes, the closest objects to the
camera are a finite distance away, and so the first bins of the SPAD
measurement contain only background counts without any backscattered
signal. We can therefore estimate the
average number of background and noise counts $\hat{b}$ as 
%
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
%
where we choose the number of bins $N$ to correspond to time
values before the backscattered signal arrives.

@@

Specifically, we identify the first and last bins that record backscattered signal
photons by locating discontinuities in the recorded counts~\cite{Xin2019}. An initial spike in
the measurements at bin $n_\text{first}$ results from the onset of backscattered
signal from the closest object, and a steep dropoff occurs after bin
$n_\text{last}$ after backscattered photons from the
furthest object are recorded. 
We estimate $n_\text{first}$ and $n_\text{last}$ by calculating  
first order differences of the transient $d[n] = \abs{h[n] - h[n+1]}$. 
\edit{For a moderate number of background counts, each background bin $h[n]$ can be
approximated as a Gaussian with mean and variance $b$, and thus $h[n] - h[n+1]$ can be approximated  
as a Gaussian with mean $0$ and variance $2b$.} We identify candidate discontinuities
$\mathcal{E}$ with a threshold on the measured differences:
%
\begin{equation}
  \mathcal{E} = \mset{n}{d[n] > \beta\sqrt{2\hat b}}.
  \label{eq:edge_set}
\end{equation}
We find that $\beta = 5$ yields good results across both simulated and captured
data.

Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
Then, we refine these estimates by selecting the closest bins that remain above
a threshold $\tau$ such that
\begin{equation}
    \begin{split}
        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
            \cdots, h[n'_\text{first}] > \tau\}\\
        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
    \cdots, h[n-1] > \tau, h[n] > \tau\}.
    \end{split}
\end{equation}
The remaining ambient counts are discarded by setting the recorded counts to
zero for all bins where \edit{$n < \hat n_\text{first}$} and $n > \hat n_\text{last}$. We use 
$\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.

%Finally, we reject all photons outside of the valid range by
%clamping those bins to 0, and we subtract our ambient estimate from the photons
%within the valid range:
%\begin{equation}
%  h'_{clean}[n] = \begin{cases}
%    0 & n < \hat n_{first} \\
%    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
%    0 & n > \hat n_{last} \\
%  \end{cases}.
%  \label{eq:h_clean}
%\end{equation}

\vspace{0.8em}\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying
the transient
by the distance-dependent scaling factor,
%
\begin{equation}
    h'[n] = h[n] \cdot z_n^2.
  \label{eq:h_scaled}
\end{equation}
%
Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our prototype.

\vspace{0.8em}\noindent{\bf Transient Re-binning.}
Last, we re-bin the transient so that the bin widths increase for increasingly
distant objects. We select the Spacing-Increasing Discretization
(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
exponential function, allocating more bins to closer distances and fewer
bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
%
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad\text{for}\qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
%
This rebinning procedure allows us to use a reduced number of bins by the histogram
matching, reducing computation time while maintaining accuracy.
\edit{For the simulated results we use $K = 140$ bins with $(\ell,
u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
n_{\text{last}}$ respectively.}
 The output of the rebinning procedure is the
target histogram $h_\text{target}$ which we use for histogram matching.

@@

The input depth map cannot be directly histogram-matched to the target histogram
because the target histogram incorporates the spatially varying reflectance of
the scene. To account for reflectance in the histogram matching procedure,
we use the normalized image color channel closest to the laser wavelength as an
estimate of the reflectance and compute a reflectance-weighted depth histogram
$h_\text{source}$;
instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
at the corresponding depth, we add the estimated reflectance value of the pixel
to the histogram bin. \edit{We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}

We match the re-binned histogram $h_\text{source}$ to $h_\text{target}$ using the method of
Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement
matrix $T$ such that $T[m, n]$ is the fraction of $h_\text{source}[m]$ that should be
moved to $h_\text{target}[n]$. \edit{We refer the reader to the supplement for
  pseudocode.} Intuitively, the procedure starts from the first bin of the
source histogram and distributes its contents to the first bins of the target
histogram, with successive source histogram bins being shifted to successive
target bins in sequence.

@@

\edit{Pseudo-code for this procedure is included in the supplement; we will make source code and data available.}

>>>>

In this section, we describe the image formation of a diffused pulsed laser and
time-resolved detector. Although our model is derived for the specific case of
imaging with a single-photon avalanche diode (SPAD), the resulting image
formation model equally applies to other time-resolved detectors. We also
describe an approach for correcting a depth map generated with a monocular depth
estimator to match the global scene information captured by the transient.

\subsection{Image Formation Model of a Diffused SPAD}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{method_eccv.pdf}
  \caption{Overview of processing pipeline. The processing pipeline uses the
    input transient measurement and an RGB image to produce an accurate depth
    map. The transient is preprocessed to adjust for ambient photon detections,
    radiometric falloff factors, and to calibrate the bin widths. From the RGB
    image, an MDE estimates an initial depth map and the scene reflectance is
    estimated. A reflectance-weighted depth histogram is compared to the
    processed transient to calculate a histogram matching matrix which is used
    to output the corrected depth.
  }
  \label{fig:pipeline}
\end{figure}

Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
scene as a distance map $z(x, y)$, where each of the 3D points has also some
unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
interreflections of the emitted light within the scene, a single-pixel diffused
SPAD integrates light scattered back from the scene onto the detector as
%
\begin{equation}
	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
	\label{eq:pulse_integral} 
\end{equation}  
%
where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
diffused light, and we assume that the light is diffused uniformly over the
scene points. Each time such a light pulse is emitted into the scene and
scattered back to the detector, the single-pixel SPAD time-stamps up to one of
the returning photons with some probability. The process is repeated millions of
times per second with the specific number of emitted pulses being controlled by
the repetition rate of the laser. As derived in previous work, the resulting measurement
can be modeled as an inhomogeneous Poisson process
$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}. Each detected photon arrival event is
discretized into a histogram $h$ of the form
%
\begin{equation}
  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
	\label{eq:spad_measurements}
\end{equation}
%
where $[n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
is a function that models the temporal uncertainty in the detector, and $b$
represents background detections from ambient light and false positive detections known as \textit{dark
count}. Like previous work, we neglect scene interreflections
and confine ourselves to the low-flux condition (where the number of photon
detections is controlled to be much smaller than the number of emitted pulses)
to avoid pileup~\cite{Shin2016}. Finally, we adopt the term
\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.

@@

\noindent{\bf Background Subtraction.}
In the first step, we remove the background counts from the
transient by initially estimating the average amount of background counts
in each time bin. For nearly all natural scenes, the closest objects to the
camera are a finite distance away, and so the first bins of the SPAD
measurement contain only background counts without any backscattered
signal. We can therefore estimate the
average number of background and noise counts $\hat{b}$ as 
%
\begin{equation}
  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
  \label{eq:ambient_estimate}
\end{equation}
%
where we choose the number of bins $N$ to correspond to time
values before the backscattered signal arrives.

@@

Specifically, we identify the first and last bins that record backscattered signal
photons by locating discontinuities in the recorded counts~\cite{Xin2019}. An initial spike in
the measurements at bin $n_\text{first}$ results from the onset of backscattered
signal from the closest object, and a steep dropoff occurs after bin
$n_\text{last}$ after backscattered photons from the
furthest object are recorded. 
We estimate $n_\text{first}$ and $n_\text{last}$ by calculating  
first order differences of the transient $d[n] = \abs{h[n] - h[n+1]}$. 
For a moderate number of background counts, each background bin $h[n]$ can be
approximated as a Gaussian with mean and variance $b$, and thus $h[n] - h[n+1]$ can be approximated  
as a Gaussian with mean $0$ and variance $2b$. We identify candidate discontinuities
$\mathcal{E}$ with a threshold on the measured differences:
%
\begin{equation}
  \mathcal{E} = \mset{n}{d[n] > \beta\sqrt{2\hat b}}.
  \label{eq:edge_set}
\end{equation}
We find that $\beta = 5$ yields good results across both simulated and captured
data.

Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
Then, we refine these estimates by selecting the closest bins that remain above
a threshold $\tau$ such that
\begin{equation}
    \begin{split}
        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
            \cdots, h[n'_\text{first}] > \tau\}\\
        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
    \cdots, h[n-1] > \tau, h[n] > \tau\}.
    \end{split}
\end{equation}
The remaining ambient counts are discarded by setting the recorded counts to
zero for all bins where $n < \hat n_\text{first}$ and $n > \hat n_\text{last}$. We use
$\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.

\noindent{\bf Falloff Compensation.}
In the second step, we compensate for distance falloff effects by multiplying
the transient
by the distance-dependent scaling factor,
%
\begin{equation}
    h'[n] = h[n] \cdot z_n^2.
  \label{eq:h_scaled}
\end{equation}
%
Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
corresponding to bin $n$, and this radiometric falloff model is consistent with
measurements captured with our prototype.

\noindent{\bf Transient Re-binning.}
Last, we re-bin the transient so that the bin widths increase for increasingly
distant objects. We select the Spacing-Increasing Discretization
(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
exponential function, allocating more bins to closer distances and fewer
bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
given by the following equation,
parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
%
\begin{equation}
  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad\text{for}\qquad i = 0,\ldots, K.
  \label{eq:sid_bin_edges}
\end{equation}
%
This rebinning procedure allows us to use a reduced number of bins \edit{in} the
histogram matching, reducing computation time while maintaining accuracy.
For the simulated results we use $K = 140$ bins with $(\ell,
u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
n_{\text{last}}$ respectively.
 The output of the rebinning procedure is the
target histogram $h_\text{target}$ which we use for histogram matching.

@@

The input depth map cannot be directly histogram-matched to the target histogram
because the target histogram incorporates the spatially varying reflectance of
the scene. To account for reflectance in the histogram matching procedure,
we use the normalized image color channel closest to the laser wavelength as an
estimate of the reflectance and compute a reflectance-weighted depth histogram
$h_\text{source}$;
instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
at the corresponding depth, we add the estimated reflectance value of the pixel
to the histogram bin. We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.

We match the re-binned histogram $h_\text{source}$ to $h_\text{target}$ using the method of
Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement
matrix $T$ such that $T[m, n]$ is the fraction of $h_\text{source}[m]$ that should be
moved to $h_\text{target}[n]$. We refer the reader to the supplement for
  pseudocode. Intuitively, the procedure starts from the first bin of the
source histogram and distributes its contents to the first bins of the target
histogram, with successive source histogram bins being shifted to successive
target bins in sequence.

@@

Pseudo-code for this procedure is included in the supplement; we will make source code and data available.

### 2020-07-19 paper/eccv2020CR/final/3668/sections/related.tex
Final camera-ready submission.

The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the transient measurement with the
output of a monocular depth estimator using a histogram matching technique.
\edit{While other recent work also explored RGB-SPAD sensor
fusion~\cite{Lindell2018,sun2020spadnet},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.}

>>>>

The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the transient measurement with the
output of a monocular depth estimator using a histogram matching technique.
\edit{While other recent work also explored RGB-SPAD sensor
fusion~\cite{Lindell2018,sun2020spadnet,ahmad2020extensible},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.}

### 2020-07-19 paper/eccv2020CR/supplement.tex
Final camera-ready submission.

\section{Radiometric calculation}
Assuming an indoor scene with fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of
5 for a diffuse scene at $R = 3$ m and a field of view of
$\theta = 40^\circ$\textdegree can be calculated as
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation}
giving $P_{\text{min}}=21$ mW. We note that this is significantly
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.

>>>>

\section{Radiometric calculation}
Assuming an indoor scene with fluorescent bulbs and an ambient spectral irradiance of $I_A =
1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of
5 for a diffuse scene at $R = 3$ m and a field of view of
$\theta = 40^\circ$ can be calculated as
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation}
giving $P_{\text{min}}=21$ mW. We note that this is significantly
less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.
